\bf Supplementary Material: What is the Best Way to Display Two Time Series to Read Association?

### 2016-02-09 paper/paper.Rnw
editing

#sasdata <- select(full.sub, rabs, n, alpha, rsgn, smoothed, design, subj_id, weights, correct, log_time)
#sasdata <- mutate(sasdata, rabs = as.numeric(rabs),
#                   subj_id = as.numeric(subj_id),
#                   design = ifelse(design=="Scatterplot", 1, 0))
#write.csv(sasdata, "sas/sasdata.csv", row.names = FALSE)
#The code that is exported to fit the model into SAS, see sas/model fit.sas

>>>>

#sasdata <- select(full.sub, rabs, n, alpha, rsgn, smoothed, design, subj_id, weights, correct, log_time)
#sasdata <- mutate(sasdata, rabs = as.numeric(rabs),
#                   subj_id = as.numeric(subj_id),
#                   design = ifelse(design=="Scatterplot", 1, 0))
#write.csv(sasdata, "sas/sasdata.csv", row.names = FALSE)
#The code that is exported to fit the model into SAS, see code/fitting model.sas

### 2016-02-09 paper/supplementary.Rnw
editing

Where $m = 20$, the number of plots in a linup, $s_{ij}$ is the number of selections made by subject $i$ on lineup $j$ and $\mathbbm{I}_{ij} = 1$ if the true plot is detected, $0$ otherwise. The most selections made on any lineup evaluation is 8.

@@

\begin{figure}[htbp]
\centering
<<multiselect, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE, fig.height=4>>=
m.select <- summarise(group_by(subset(full.sub, attempts>1), subj_id, pic_id), attempts=max(attempts))
m.freq <- data.frame(table(m.select$pic_id))
m.lineup <- merge(m.freq, bylineup, by.x="Var1", by.y="pic_id")
ggplot(data=m.lineup) + geom_bar(aes(x=factor(r), fill=design)) + facet_grid(n~smoothed) + labs(y="Count", x="True plot correlation")
@
\caption{Characteristics of lineups with at least one subject making multiple selections. Overlaid line lineups have multiple selections more often, and true plot correlation does not appear to have an impact except at large sample sizes.}
\label{lineupmulti}
\end{figure}

\begin{table}[h]
\centering
\caption{Number of times $n$ selections from a lineup evaluation were made. The subject who made the most selections is additionally reported. There is no relationship between a subject's demographics and a likelihood to make multiple selections.}
\label{table}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

@@

Analysing the level one residuals, $\hat{\epsilon_{i}}$, and level two residuals, $\hat{\gamma_{i}}$, allows us to test the model fit as described \citet{Loy}. There are some negative extreme outliers but the distributional assumptions appear to hold.

@@

$${E[score]}_{i} = \frac{1}{K}\sum_{j}{score}_{ij}$$

@@

$${E[score]}_{j} = \sum_{i}\{{E[score]}_{i} | i \in L_{j}\}$$

Finally, we measure visual ability by:

$${Visual Ability}_{j} = {score}_{j}-{E[score]}_{j}$$.

>>>>

Where $m = 20$, the number of plots in a linup, $s_{ij}$ is the number of selections made by subject $i$ on lineup $j$ and $\mathbbm{I}_{ij} = 1$ if the true plot is detected, $0$ otherwise. The most selections made on any lineup evaluation is 8. No subject demographic had an increased rate of making multiple selections.

@@

We originally hypothesised that factor combinations with a low power are most likely to have multiple selections due to a decreased ability to differentiate between true and null plots. This would cause most lineups with multiple selection lineups to be concentrated around $\rho = \pm 0.3$ for both designs as well as any negative value for overlaid line graphs. Figure ~\ref{lineupmulti} plots lineups with at least one case of a subject selecting multiple plots in an evaluation. The hypothesised effect only appears at sample sizes of 48 and 96. The overlaid line graph lineups were more likely to have multiple selections, but this is also occuring in high positive correlations, where the power was similar to that of a scatter plot.

\begin{figure}[h]
\centering
<<multiselect, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE, fig.height=4>>=
m.select <- summarise(group_by(subset(full.sub, attempts>1), subj_id, pic_id), attempts=max(attempts))
m.freq <- data.frame(table(m.select$pic_id))
m.lineup <- merge(m.freq, bylineup, by.x="Var1", by.y="pic_id")
ggplot(data=m.lineup) + geom_bar(aes(x=factor(r), fill=design)) + facet_grid(n~smoothed) + labs(y="Count", x="True plot correlation")
@
\caption{Characteristics of lineups with at least one subject making multiple selections. Overlaid line graph lineups have subjects make multiple selections more often, but true plot correlation does not appear to have an impact except at large sample sizes.}
\label{lineupmulti}
\end{figure}

\begin{table}[h]
\centering
\caption{Number of times $n$ selections from a lineup evaluation were made. The subject who made the most plot selections within their ten evaluations is additionally reported. There is no relationship between a subject's demographics and a likelihood to make multiple selections.}
\label{table}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

@@

Analysing the level one residuals, $\hat{\epsilon_{i}}$, and level two residuals, $\hat{\gamma_{i}}$, allows us to test the model fit as described by \citet{Loy}. There are some extreme negative outliers but the distributional assumptions appear to hold.

@@

$$E[{score}_{i}] = \frac{1}{K}\sum_{j}{score}_{ij}$$

@@

$$E[{score}_{j}]  = \sum_{i}\{E[{score}_{i}] | i \in L_{j}\}$$

Finally, we proxy visual ability by:

$${Visual Ability}_{j} = {score}_{j}-E[{score}_{j}] $$.
